% Original author:
% Alessandro Plasmati
%
% Modified by:
% Louis Pilfold
%
% License:
% CC BY-NC-SA 3.0
% http://creativecommons.org/licenses/by-nc-sa/3.0/

%--------------------------------------------%
% Packages and other document configurations %
%--------------------------------------------%

\documentclass[a4paper 11pt]{scrartcl}

% Move the margin to the left of the page
\reversemarginpar

% New command defining the margin text style
\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}}

% Use the classicthesis style for the style of the document
\usepackage[nochapters]{classicthesis}
% Use the currvita style for the layout of the document
\usepackage[LabelsAligned]{currvita}

\renewcommand{\cvheadingfont}{\color{Maroon}}

% Required for adding links and customizing them
\usepackage{hyperref}
% Set link colors
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon}

% Set the width of the date box in each block
\newlength{\datebox}\settowidth{\datebox}{2014 01 onwards}

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0
  \parbox{\datebox}{\small \textit{#1}}\hspace{0.3em} #2 #3
% Define a command for each new block - change spacing and font sizes here:
%   #1 is the left margin
%   #2 is the italic date field and
%   #3 is the position/employer/location field

% Add some white space after each new entry
\vspace{1.0em}}

% Define a command for descriptions of each entry
% - change spacing and font sizes here
\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright
  \footnotesize{#1}\par\normalsize\vspace{1em}}

\usepackage[utf8]{inputenc}
%------------------------------------------------------------------------------

% Remove date from end of document
\date{}

\begin{document}

% Remove page numbering
\pagenumbering{gobble}

%----------------------------%
% Name & contact information %
%----------------------------%

\begin{cv}{\spacedallcaps{Louis Adam Pilfold}}\vspace{1.5em}

\noindent\spacedlowsmallcaps{Personal Information}\vspace{1.0em}

\NewEntry{phone}{+44 (0)7378 350 639}

\NewEntry{email}{\href{mailto:louis@lpil.uk}{louis@lpil.uk}}

\NewEntry{website}{\href{https://lpil.uk}{lpil.uk}}

\NewEntry{projects}{\href{https://github.com/lpil}{github.com/lpil}}

\vspace{0.5em}


\noindent\spacedlowsmallcaps{Summary}\vspace{1em}

\Description{An enthusiastic developer looking to help a team build
  efficient and maintainable systems that bring real business value.}
\vspace{0.5em}

\Description{\MarginText{Core Technologies}Elixir, Erlang, OCaml, Javascript,
  Elm, ReactJS, Ruby, Rust, Haskell, AWS, GCP, Terraform, Ansible, Docker,
  Linux, Compilers, Type systems}

\Description{\MarginText{Core Skills}Development, Communication, Documentation,
  Empathy, Technical leadership, Coaching, Bad dancing}

\Description{\MarginText{Interests}Functional programming, Team dynamics,
  Distributed systems, Software architecture, Open source software, Test driven
  development, Digital art}

%------------------------------------------------

\vspace{0.5em} % Extra space between major sections

%-----------------%
% Work experience %
%-----------------%

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1.5em}

\NewEntry{2016.12 - present}{Tech Lead}

\Description{\MarginText{Honeycomb}Honeycomb is a leading AdTech company
  providing automated QC, transcoding and delivery of video advertising for TV
  broadcast and online. Brought on as a senior software engineer
  I was promoted after 8 months to Tech Lead, where I led the team building
  Sky UK's new programmatic delivery platform capabilities, as well as our new
  micro-services architecture. Following successful delivery of HVL I have been
  working in a two person team rebuilding our infrastructure to be automated,
  elastic, and multi-cloud, directed by current business needs.
  \newline In addition to delivery focused work as a member of tech management
  I was also responsible for client interaction, pastoral care and support of
  team members, and managing the hiring process. I took over as interim Head of
  Architecture for 3 months while my colleague recovered from surgery.
}

\vspace{0.5em}

\NewEntry{2016.04 - 2016.11}{Software Engineer}

\Description{\MarginText{Red Badger}Red Badger is a leading digital consultancy
  with a focus on user experience, delivery, and cutting edge open source
  software. I was a full stack engineer working primarily with Javascript and
  AWS. Projects include Tesco's new online grocery store, Red Badger's new
  website, the React London community site, and internal proof of
  concepts for prospective clients.
}

\vspace{0.5em}


\NewEntry{2015.08 - 2016.04}{Web Developer}

\Description{\MarginText{ROLI}ROLI is a start up pushing the boundaries of
  music expression with ground breaking new hardware and software instruments.
  I worked as a back end engineer and DevOps, maintaining ROLI's Rails based
  APIs and leading the migration of all ROLI applications to AWS. I introduced
  best practices such as automated testing and CI/CD to the newly formed web
  team.
}

\vspace{0.5em}

\vspace{1.0em} % bump onto next page

\NewEntry{2015.01 - 2015.08}{Ruby Developer}

\Description{\MarginText{Reevoo}Reevoo is a pioneering ratings and reviews
  provider, with clients such as Kia, British Gas, and Nintendo.
  I was a back end engineer working with the large legacy applications written
  with the Rails and Grape Ruby frameworks.
}

\vspace{0.5em}


\NewEntry{2013.04 - 2014.12}{Software Product Developer}

\Description{\MarginText{Perivan Solutions}Perivan Solutions is a FinTech
  software-as-a-service company that provides technical solutions to companies
  such as St James's Place Wealth Management, AXA Group, and Schroders PLC.
  I worked as a full stack engineer for Perivan's B2B applications.
}

%------------------------------------------------

\vspace{1.0em} % Extra space between major sections

%----------%
% Speaking %
%----------%

\spacedlowsmallcaps{Public Speaking}\vspace{1em}

\Description{\MarginText{2017.08}Getting Pretty Serious
  $\cdotp$\
  Elixir LDN 2017 Conference
}

\Description{\MarginText{2016.09}Build Your Own Elixir
  $\cdotp$\
  Elixir LDN 2016 Conference
}

\Description{\MarginText{2016.05}Fashioning a Faster Feedback Loop
  $\cdotp$\
  Elixir Meetup at GoCardless
}

%----------%
% Projects %
%----------%

\vspace{1.0em} % Extra space between major sections

\spacedlowsmallcaps{Notable Open Source Projects}\vspace{1em}

\Description{\MarginText{Gleam}A functional language that compiles to Erlang bytecode
  \newline
  \href{https://github.com/lpil/gleam}{https://github.com/lpil/gleam}
}

\Description{\MarginText{exfmt}An opinionated auto-formatter for the Elixir language
  \newline
  \href{https://github.com/lpil/exfmt}{https://github.com/lpil/exfmt}
}

\Description{\MarginText{Dogma}A code style linter for the Elixir language
  \newline
  \href{https://github.com/lpil/dogma}{https://github.com/lpil/dogma}
}

\Description{\MarginText{mix test.watch}An automatic test runner for
  Elixir and Erlang
  \newline
  \href{https://github.com/lpil/mix-test.watch}{https://github.com/lpil/mix-test.watch}
}

%---------%
% Courses %
%---------%

% \vspace{1.0em} % Extra space between major sections

% \spacedlowsmallcaps{Courses}\vspace{1em}

%------------------------------------------------


% \Description{\MarginText{University of Illinois}Cloud Computing Concepts 1
%   \newline
%   Q4 2016 - Distributed Systems
% }

% \Description{\MarginText{Kent Uni}Functional Programming with Erlang MOOC
%   \newline
%   Q2 2015 - Erlang
% }

% \Description{\MarginText{EFPL}Principles of Reactive Programming
%   \newline
%   Q1 2015 - Scala
% }

% \Description{\MarginText{DelftX}Introduction to Functional Programming
%   \newline
%   Q4 2014 - Haskell
% }

% \Description{\MarginText{EPFL}Functional Programming Principles in Scala
%   \newline
%   Q3 2014 - Scala
% }

% \Description{\MarginText{BerkeleyX}Engineering Software as a Service Part 2
%   \newline
%   Q2 2014 - Ruby, Rails, Coffeescript
% }

% \Description{\MarginText{BerkeleyX}Engineering Software as a Service Part 1
%   \newline
%   Q1 2014 - Ruby, Rails
% }

% \Description{\MarginText{MITx}Introduction to Computer Science and Programming
%   Using Python
%   \newline
%   Q1 2013 - Python
% }

%------------------------------------------------

\vspace{1.0em} % Extra space between major sections

%-----------%
% Education %
%-----------%

\spacedlowsmallcaps{Educational Qualifications}\vspace{1em}

\Description{\MarginText{MOOC Platforms}2013-2016
  \newline
  8 computer science courses, full list available upon request}

\Description{\MarginText{The University of Brighton}2010-2013
  \newline
  Certificate of Higher Education $\cdotp$\ Biological Sciences}

\Description{\MarginText{The Henley College}2008-10
  \newline
  3 A Levels}

\Description{\MarginText{Herschel Grammar School}2002-2007
  \newline
  11 GCSEs}

%------------------------------------------------

\vspace{1.0em} % Extra space between major sections

%-------------------%
% Other information %
%-------------------%

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Volunteering}I coach programming at Railsgirls,
  Codebar, Trans*code and other events facilitating women, LGBTQ people,
  and other underrepresented groups in engineering and the technology
  industry.
}

\Description{\MarginText{Other Interests}Collecting music
  \ $\cdotp$\ \ Social ethics \& equality
  \ $\cdotp$\ \ Shoes with toes
}

\end{cv}

\end{document}
