% Original author:
% Alessandro Plasmati
%
% Modified by:
% Louis Pilfold
%
% License:
% CC BY-NC-SA 3.0
% http://creativecommons.org/licenses/by-nc-sa/3.0/

%--------------------------------------------%
% Packages and other document configurations %
%--------------------------------------------%

\documentclass[a4paper 11pt]{scrartcl}

% Move the margin to the left of the page
\reversemarginpar

% New command defining the margin text style
\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}}

% Use the classicthesis style for the style of the document
\usepackage[nochapters]{classicthesis}
% Use the currvita style for the layout of the document
\usepackage[LabelsAligned]{currvita}

\renewcommand{\cvheadingfont}{\color{Maroon}}

% Required for adding links and customizing them
\usepackage{hyperref}
% Set link colors
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon}

% Set the width of the date box in each block
\newlength{\datebox}\settowidth{\datebox}{2014 01 onwards}

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0
  \parbox{\datebox}{\small \textit{#1}}\hspace{0.3em} #2 #3
% Define a command for each new block - change spacing and font sizes here:
%   #1 is the left margin
%   #2 is the italic date field and
%   #3 is the position/employer/location field

% Add some white space after each new entry
\vspace{1.0em}}

% Define a command for descriptions of each entry
% - change spacing and font sizes here
\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright
  \footnotesize{#1}\par\normalsize\vspace{1em}}

\usepackage[utf8]{inputenc}
%------------------------------------------------------------------------------

% Remove date from end of document
\date{}

\begin{document}

% Remove page numbering
\pagenumbering{gobble}

%----------------------------%
% Name & contact information %
%----------------------------%

\begin{cv}{\spacedallcaps{Louis Adam Pilfold}}\vspace{1.5em}

\noindent\spacedlowsmallcaps{Personal Information}\vspace{1.0em}

\NewEntry{phone}{+44 (0)7378 350 639}

\NewEntry{email}{\href{mailto:louis@lpil.uk}{louis@lpil.uk}}

\NewEntry{website}{\href{https://lpil.uk}{lpil.uk}}

\NewEntry{projects}{\href{https://github.com/lpil}{github.com/lpil}}

\vspace{0.8em}

% \noindent\spacedlowsmallcaps{Summary}\vspace{0.8em}
%
% \Description{An enthusiastic developer looking to help a team build
%   efficient and maintainable systems that bring real business value.}
% \vspace{0.5em}

\Description{\MarginText{Core Technologies}Gleam, Rust, Elixir, Erlang, Go,
  JavaScript, Haskell, Elm, PostgreSQL, AWS, Linux, CI/CD, containers,
  infrastructure as code, compilers, type systems.}

\Description{\MarginText{Core Skills}Development, communication, documentation,
  system design, software architecture, empathy, testing, technical leadership,
  coaching, bad dancing.}

%------------------------------------------------

\vspace{0.8em} % Extra space between major sections

%-----------------%
% Work experience %
%-----------------%

\noindent\spacedlowsmallcaps{Work Experience}\vspace{0.8em}

\NewEntry{2018.01 - present}{Creator, Lead Developer}

\Description{\MarginText{Gleam}Gleam is a high scalable, statically typed,
  functional programming language for the Erlang VM, for which I am the
  creator and community leader. Gleam is open source, used in production, and
  financed by sponsorship via GitHub.
}

\vspace{0.5em}

\NewEntry{2021.05 - present}{Software Engineering Consultant}

\Description{\MarginText{Kalda}Kalda is a LGBTQIA+ wellness community and
early stage start-up. I guided Kalda through the design, development, and
delivery of their web platform and mobile applications so that they can secure
further investment.
}

\vspace{0.5em}

\NewEntry{2020.10 - 2021.05}{Contract Open Source Engineer}

\Description{\MarginText{Embark Studios}Embark is a pioneering video game studio
investing heavily into ML and Rust. I worked on their new Rust game engine, Rust
web services, developer tooling, and Kubernetes deployments.
}


\vspace{0.5em}

\NewEntry{2020.03 - 2020.05}{Contract Software Engineer}

\Description{\MarginText{FetLife}FetLife are a high traffic social network.
  I implemented their new video player and text editor using statically typed
  Ruby and TypeScript, using extensive A/B testing to iterate on designs in
  order to provide the most engaging user experience.
}

\vspace{0.5em}

\NewEntry{2019.05 - 2020.03}{Contract Platform Engineer}

\Description{\MarginText{Nationwide Building Society}Nationwide is a mutual
  financial institution and the largest building society in the world. I worked
  on fully automated provisioning of secure and compliant environments using
  Golang, Kubernetes, and AWS. I designed and lead the implementation of the
  production readiness analyser for these environments.
}

\vspace{0.5em}

\NewEntry{2018.08 - 2020.10}{Founder, CTO}

\Description{\MarginText{Waive Hello}Waive is a rights management tool for the
  advertising industry. As technical founder I was responsible for all product
  design and delivery. The product was built using Elixir, Erlang, Elm, PostgreSQL,
  and GCP.
}
\vspace{0.5em}

\NewEntry{2016.12 - 2018.08}{Tech Lead}

\Description{\MarginText{Honeycomb TV}Honeycomb was a leading broadcast
  ad delivery platform, built using Rails and Elixir. I led the team building
  Sky UK's new video delivery pipeline, handled client interaction, and
  managing the hiring process. For 3 months I served as Head of Architecture
  while my colleague recovered from surgery.
}

\vspace{0.5em}

\NewEntry{2016.04 - 2016.11}{Software Engineer}

\Description{\MarginText{Red Badger}Red Badger is a leading digital
  consultancy. I was a full stack engineer working primarily with JavaScript
  and AWS for clients including Tesco and Santander.
}

% \vspace{0.5em}
\vspace{0.5em} % push onto next page

\NewEntry{2015.08 - 2016.04}{Web Developer}

\Description{\MarginText{ROLI}ROLI is a start-up making ground breaking new
  musical instruments. I worked as a backend and DevOps engineer, maintaining
  ROLI's web applications, and leading the migration to AWS.
}

\vspace{0.5em}

\NewEntry{2015.01 - 2015.08}{Ruby Developer}

\Description{\MarginText{Reevoo}Reevoo is an high traffic ratings and reviews
provider. I was a backend engineer working with Ruby web applications, deployed
to AWS EC2.
}

\vspace{0.5em}

\NewEntry{2013.04 - 2014.12}{Software Product Developer}

\Description{\MarginText{Perivan Solutions}Perivan Solutions is a FinTech
  software-as-a-service company providing document management solutions.
  I worked as a full stack engineer working on Ruby APIs and sysadmin working
  with Linux on Digital Ocean.
}

%------------------------------------------------

% \vspace{1.0em} % Extra space between major sections

%----------%
% Projects %
%----------%

% \vspace{0.8em} % Extra space between major sections

% \spacedlowsmallcaps{Notable Open Source Projects}\vspace{0.8em}

% \Description{\MarginText{Gleam}A statically typed functional programming
% language for building concurrent systems that scale.
%   \newline
%   \href{https://github.com/lpil/gleam}{https://github.com/gleam-lang/gleam}
% }

% \Description{\MarginText{exfmt}The original code formatter for the Elixir language.
%   \newline
%   \href{https://github.com/lpil/exfmt}{https://github.com/lpil/exfmt}
% }

% \Description{\MarginText{Dogma}A code style linter for the Elixir language.
%   \newline
%   \href{https://github.com/lpil/dogma}{https://github.com/lpil/dogma}
% }

%---------%
% Courses %
%---------%

% \vspace{1.0em} % Extra space between major sections

% \spacedlowsmallcaps{Courses}\vspace{1em}

%------------------------------------------------


% \Description{\MarginText{University of Illinois}Cloud Computing Concepts 1
%   \newline
%   Q4 2016 - Distributed Systems
% }

% \Description{\MarginText{Kent Uni}Functional Programming with Erlang MOOC
%   \newline
%   Q2 2015 - Erlang
% }

% \Description{\MarginText{EFPL}Principles of Reactive Programming
%   \newline
%   Q1 2015 - Scala
% }

% \Description{\MarginText{DelftX}Introduction to Functional Programming
%   \newline
%   Q4 2014 - Haskell
% }

% \Description{\MarginText{EPFL}Functional Programming Principles in Scala
%   \newline
%   Q3 2014 - Scala
% }

% \Description{\MarginText{BerkeleyX}Engineering Software as a Service Part 2
%   \newline
%   Q2 2014 - Ruby, Rails, Coffeescript
% }

% \Description{\MarginText{BerkeleyX}Engineering Software as a Service Part 1
%   \newline
%   Q1 2014 - Ruby, Rails
% }

% \Description{\MarginText{MITx}Introduction to Computer Science and Programming
%   Using Python
%   \newline
%   Q1 2013 - Python
% }

%------------------------------------------------

%-----------%
% Education %
%-----------%

\vspace{0.8em} % Extra space between major sections

\spacedlowsmallcaps{Educational Qualifications}\vspace{0.8em}

\Description{\MarginText{MOOC Platforms}2013-2016
  \newline
  8 computer science courses from universities such as MIT, EPFL, Berkley and
  the University of Kent. Full list available upon request.}

\Description{\MarginText{The University of Brighton}2010-2013
  \newline
  Certificate of Higher Education $\cdotp$\ Biological Sciences}

\Description{\MarginText{The Henley College}2008-10
  \newline
  3 A Levels}

\Description{\MarginText{Herschel Grammar School}2002-2007
  \newline
  11 GCSEs}

%------------------------------------------------

%-------------------%
% Other information %
%-------------------%

\vspace{0.8em} % Extra space between major sections

\spacedlowsmallcaps{Other Information}\vspace{0.8em}

\Description{\MarginText{Public Speaking}I frequently speak at conferences and
technology events such as Code Mesh, Code BEAM, and Elixir LDN. A
full list of my talks can be found on my website.
}

\Description{\MarginText{Volunteering}I coach programming at Railsgirls,
  Codebar, Trans*code and other events aimed at helping underrepresented groups
  in technology.
}

\Description{\MarginText{Other details}Dual Irish and British citizenship
  \ $\cdotp$\ \ Full UK driving licence holder
}

\Description{\MarginText{Interests}Collecting music
  \ $\cdotp$\ \ Social ethics \& equality
  \ $\cdotp$\ \ Shoes with toes
}

\end{cv}

\end{document}
